Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-02-07 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
updated main tex/bib
hs: to merge

\begin{table*}[th]
\begin{tabular}{c | c c c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
\hline
sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.7$~km~\cite{Perkins:2021mhb} & \dots \\
dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~\cite{Silva:2020acr}   & \dots \\
cEFTofGR & 4 & $-0.3680$ / $-0.5131$  & 1.9242 / 1.7000 & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of the quasinormal modes calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
references from which we used the results from and the current best constraint
(if applicable).
%
In the entries for cEFTofGR, the first entries in the $\delta
\omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
\emph{only parity-even correnctions} and the second entries by considering
\emph{only parity-odd corrections}. In these cases, the dimensionless parameters
$\lambda_{\rm e,o}$ are degenerate with the lengthscale $\ell$.
%
\hs{Add a column with the constraint (if any) that we placed.}
\hs{TODO: add which runs are done and which need to be done.}
}
\label{tab:ref_theories_qnms}
\end{table*}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
\caption{Posterior probability distribution on $\ell_{\rm CS}$ with GW200129.
The posterior shows that information was gained on this parameter relative to
the initial uniform prior distribution $\ell_{\rm CS} \in [0,\, 200]$~km.
%
The vertical lines represent two threshold for the validity of the theory as
an EFT.
%
The dotted line (labelled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
given by the median value of the secondary's mass $\epsilon \, (G m_2 / c^2)$.
%
The dot-dashed line (labelled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
given by the median value of the remnant's mass $\epsilon \, (G M_{f} / c^2)$.
%
For both, we used $\epsilon = 0.5$.
%
If we take the latter as a lengthscale for the validity of dCS as an EFT, we
have place upper bound on $\ell_{\rm CS} \leqslant 43.8$, within the
approximation of our formalism.
}
\label{fig:dCS_bounds}
\end{figure}

>>>>

\begin{table*}[th]
\begin{tabular}{c | c c c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
\hline
sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.7$~km~\cite{Perkins:2021mhb} & \dots \\
dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~\cite{Silva:2020acr}   & \dots \\
cEFTofGR & 4 & $-0.3680$ $(-0.5131)$  & 1.9242 (1.7000) & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of the quasinormal modes calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
references from which we used the results from and the current best constraint
(if applicable).
%
In the entries for cEFTofGR, the first entries in the $\delta
\omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
\emph{only parity-even corrections} and the second entries by considering
\emph{only parity-odd corrections}. In these cases, the dimensionless parameters
$\lambda_{\rm e,o}$ are degenerate with the length scale $\ell$.
%
\hs{Add a column with the constraint (if any) that we placed.}
\hs{TODO: add which runs are done and which need to be done.}
}
\label{tab:ref_theories_qnms}
\end{table*}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
\caption{Posterior probability distribution on $\ell_{\rm CS}$ with GW200129.
The posterior shows that information was gained on this parameter relative to
the initial uniform prior distribution $\ell_{\rm CS} \in [0,\, 200]$~km.
%
The vertical lines represent two threshold for the validity of the theory as
an EFT.
%
The dotted line (labelled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
given by the median value of the secondary's mass $\varepsilon \, (G m_2 / c^2)$.
%
The dot-dashed line (labelled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
given by the median value of the remnant's mass $\varepsilon \, (G M_{f} / c^2)$.
%
For both, we used $\varepsilon = 0.5$.
%
If we take the latter as a length scale for the validity of dCS as an EFT, we
have place upper bound on $\ell_{\rm CS} \leqslant 43.8$~km, within the
approximation of our formalism.
}
\label{fig:dCS_bounds}
\end{figure}
